### 2021-09-15 sections/healthcare_application/main.tex
Section: ED-EMS application (#11)
* Add ARD with PoA plots in imgs/ directory

Each added pdf has four plots on it:
- Asymmetric replicator dynamics stratgies for row player
- Asymmetric replicator dynamics stratgies for column player
- Blocking time price of anarchy over time for row player
- Blocking time price of anarchy over time for column player

* Add initial draft of Application section

* Update known words

* Add info about asymmetric replicator dynamics

* Improve asymmetric rd plots

Increase the granularity of the PoA curve so that it looks nicer

* Add jupyter notebook for the ba

There are numerous new articles that focus on the problems that arise when 
ambulances stay parked outside of the hospital for a long amount of time
\cite{dailyrecords}, \cite{staffordshirelive}.
Some news reports also comment on the long idle time of ambulances when 
they are not in use \cite{herefordtimes} and there are several reports of 
examples where this became an issue for new patients \cite{southwalesargus}.

@@

Although the Nash equilibria is a great theoretical measure it sometimes may be
% TODO: great theoretical measure?
inconsistent with our intuitive notions about what should be the outcome of a 
game \cite{myerson1978refinements}.
Therefore it might not be the best way to describe human behaviour.
Since the work of Maynard Smith \cite{smith1986evolutionary} evolutionary game 
theory gives the tools for the emergence of stable behaviour.
One such model that allows for asymmetric payoffs, as is the case above, is 
replicator dynamics.
Stable outcomes of this algorithm will correspond to a subset of Nash
equilibria but more importantly, will give a model of emergent behaviour.

@@

\begin{equation}
    \frac{dy}{dt}_i = y_i((f_y)_i - \phi_y), \quad \text{ for all }i
\end{equation}
% TODO: Too much info?

@@

In order to analyse how efficient the strategies played at every iteration are, 
the concept of the price of anarchy is used.
Price of anarchy is a measure that is used to quantify the efficiency of a
behaviour \cite{roughgarden2005selfish}.
In other words the price of anarchy is the worst-case measure and it is
defined as:

@@

>>>>

There are numerous news articles that focus on the problems that arise when 
ambulances stay parked outside of the hospital for a long amount of time
~\cite{dailyrecords}, \cite{staffordshirelive}.
Some news reports also comment on the long idle time of ambulances when 
they are not in use~\cite{herefordtimes} and there are several reports of 
examples where this became an issue for new patients~\cite{southwalesargus}.
A particular article looked into this problem from the point of view of an 
ambulance paramedic:

\begin{quotation}
    % <!--alex ignore he-she her-him-->
    ``He knows if a patient arrives more urgently in need of help, his will be 
    pushed back''~\cite{bbcwales}

    ``We used to bring poorly patients in, and we were out on the road again in 15 minutes.''~\cite{bbcwales}
\end{quotation}

@@

Nash equilibria is a theoretical measure which can be
inconsistent with intuitive notions about what should be the outcome of a 
game \cite{myerson1978refinements}.
Therefore it might not be the best way to describe human behaviour.
Since the work of Maynard Smith \cite{smith1986evolutionary} evolutionary game 
theory gives the tools for the emergence of stable behaviour.
One such model that allows for asymmetric payoffs, as is the case above, is 
replicator dynamics.
Stable outcomes of this algorithm will correspond to a subset of Nash
equilibria but more importantly, will give a model of emergent behaviour.

@@

\begin{equation}
    \frac{dy}{dt}_i = y_i((f_y)_i - \phi_y), \quad \text{ for all }i
\end{equation}

@@

In order to analyse how efficient the strategies played at every iteration are, 
the concept of the price of anarchy is used.
Price of anarchy is a measure that is used to quantify the efficiency of a
behaviour \cite{roughgarden2005selfish}.
In other words the price of anarchy is the worst-case equilibria measure and it 
is defined as:

@@

Matrices \(A\) and \(B\) represent the original payoff matrices while matrices
\(\tilde{A}\) and \(\tilde{B}\) represent the incentivised payoff matrices.
It can be observed that matrix \(\tilde{A}\) is a scaled version of matrix 
\(A\) only on the row that is most frequently played and similarly matrix 
\(\tilde{B}\) of matrix \(B\) only on the column that is most frequently played
(matrix \(A\): row \(5\), matrix \(B\): column \(6\), see figure 
\ref{fig:ard_penalty}).
Note that the values of the payoff matrices only differ on the fourth digit
which is the raw utility of the strategies played.

\tiny
\begin{equation*}
    A = 
    \begin{bmatrix}
        0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 
        & 0.9995052 & 0.9995052 \\
        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 
        & 0.9995466 & 0.999539 \\
        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 
        & 0.9996734 & 0.999649  \\
        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
        & 0.9998909 & 0.9998517 \\
        \color{blue}0.99999996 & \color{blue}0.99999994 & \color{blue}0.99999992 
        & \color{blue}0.99999988 & \color{blue}0.99999973 & \color{blue}0.9999989 
        & \color{blue}0.9999859 \\
        0.9998773 & 0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 
        & 0.9999126 & 0.9999712
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    B = 
    \begin{bmatrix}
        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 
        & \color{red}1.0 & 0.99982128 \\
        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 
        & \color{red}0.99999997 & 0.9998333  \\
        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 
        & \color{red}0.99999966 & 0.99985269 \\
        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 
        & \color{red}0.99999921 & 0.99986701 \\
        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 
        & \color{red}0.9999972 & 0.9998958  \\
        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 
        & \color{red}0.99997106 & 0.99997276 \\
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{A} = 
    \begin{bmatrix}
        0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518
        & 0.99950518 & 0.99950518 \\
        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845
        & 0.99954656 & 0.99953879 \\
        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874
        & 0.99967339 & 0.9996492  \\
        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
        & 0.9998909 & 0.99985171 \\
        \color{blue}0.99969996 & \color{blue}0.99969994 & \color{blue}0.99969992 
        & \color{blue}0.99969988 & \color{blue}0.99969973 & \color{blue}0.99969895 
        & \color{blue}0.99968586 \\
        0.9998773 &  0.99987995 & 0.99988236 & 0.99988643 & 0.99989417
        & 0.99991264 & 0.99997122 \\
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{B} = 
    \begin{bmatrix}
        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942
        & \color{red}0.9997 & 0.99982128 \\
        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153
        & \color{red}0.99969997 & 0.9998333 \\
        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286
        & \color{red}0.99969966 & 0.99985269 \\
        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667
        & \color{red}0.99969921 & 0.99986701 \\
        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077
        & \color{red}0.9996972 & 0.9998958 \\
        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407
        & \color{red}0.99967106 & 0.99997276 \\
    \end{bmatrix}
\end{equation*}
\normalsize
